Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-16 writeup/gz_hubble_data.tex
Fixing filter curves for GOODS 5-epoch. See #91.

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
made no practical difference. If no spectroscopic redshifts were available,
the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

>>>>

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
made no practical difference. Galaxies with inconsistent spectroscopic
redshifts between any pair of catalogs are marked with a flag in
Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.
